Comparative Evaluation of Spark and Flink Stream Processing

### 2017-02-19 paper/paper.tex
added flink section

\par The processing models of Big Data are Batch and Stream processing, Batch processing is a way to handle large volumes of data (e.g., processing of historical transactions), is more concerned with throughput. While the Stream processing  is a method to manage fast and continuously incoming data (real-time), process it as it arrives (e.g., credit card fraud detection and network monitoring applications), where the low latency is required. The variety of data (structured and semi-structured) is included in the two processing models.

@@

Apache Spark is an open source project that provide general framework for large-scale data processing \cite{spark}. It offers programming API in Java, Scala, Python and R. Its stack includes set of built-in modules including Spark SQL, MLlib for machine learning, GraphX for graph processing, and Spark Streaming to process real-time data streams. It can access different data sources including Hadoop Distributed File System (HDFS), Apache Cassandra database, Apache HBase database etc.

The main data abstraction in Spark is the Resilient Distributed Datasets (RDDs), which is a in-memory collection of elements partitioned across cluster of computers that can be processed in parallel \cite{rdd}. RDDs supports two categories of operations: transformations that drive new RDDs from the operated ones (e.g., map).  And actions which return a value (e.g., count).
\section{Experiment Setup and Implementation}
This section describes the experiment workloads and their implementation in each framework.
\section{Performance Results}

@@

\bibitem[2]{spark} 
Apache Spark. Available: https://spark.apache.org/ [Accessed February 2017]

\bibitem[3]{rdd}
Zaharia, Matei, et al. "Resilient distributed datasets: A fault-tolerant abstraction for in-memory cluster computing." Proceedings of the 9th USENIX conference on Networked Systems Design and Implementation. USENIX Association, 2012.
%
\end{thebibliography}
\end{document}

>>>>

\par The processing models of Big Data are Batch and Stream processing, Batch processing is a way to handle large, finite volumes of data (e.g., processing of historical transaction records), is more concerned with throughput. While the Stream processing  is a method to manage fast and continuously incoming data (real-time), process it as it arrives (e.g., credit card fraud detection and network monitoring applications), where the low latency is required. The variety of data (structured and semi-structured) is included in the two processing models.

@@

\par Apache Spark is an open source project that provide general framework for large-scale data processing \cite{spark}. It offers programming API in Java, Scala, Python and R. Its stack includes set of built-in modules including Spark SQL, MLlib for machine learning, GraphX for graph processing, and Spark Streaming to process real-time data streams. It can access different data sources including Hadoop Distributed File System (HDFS), Apache Cassandra database, Apache HBase database etc.

\par The main data abstraction in Spark is the Resilient Distributed Datasets (RDDs), which is a in-memory collection of elements partitioned across cluster of computers that can be processed in parallel \cite{rdd}. RDDs supports two categories of operations: transformations that drive new RDDs from the operated ones (e.g., map).  And actions which return a value (e.g., count).

//TODO: DStreams

\subsection{Apache Flink}

Apache Flink is an open source project that provide large-scale, distributed stream processing platform, while the batch processing treated as special case of streaming (as finite data stream) \cite{flink}.
It offers programming API in Java, Scala. Its stack includes the core DataStream and DataSet APIs with additional libraries such as Complex event processing for Flink (FlinkCEP), Machine Learning for Flink (FlinkML), and Flink Graph API (Gelly).

The main data abstraction of Flink are DataStream and DataSet that represents read-only collection of elements of the same type. The list of elements is bounded (i.e., finite) in DataSet, while it is unbounded (i.e., infinite) in case of DataStream.

\section{Experiment Setup and Implementation}
This section describes the experiment workloads and their implementation in each framework.
\section{Performance Results}

@@

\bibitem[2]{spark} 
Apache Spark. Available: https://spark.apache.org/ [Accessed February 2017].

\bibitem[3]{rdd}
Zaharia, Matei, et al. "Resilient distributed datasets: A fault-tolerant abstraction for in-memory cluster computing." Proceedings of the 9th USENIX conference on Networked Systems Design and Implementation. USENIX Association, 2012.

\bibitem[4]{flink} 
Apache Flink. Available: https://flink.apache.org/ [Accessed February 2017].

%
\end{thebibliography}
\end{document}
